\documentclass{article}

\input{preamble}

\begin{document}

\thispagestyle{empty}

\begin{center}
    \textbf{\LARGE Namkhang Le} \\
    Namkhangnle@hotmail.com $|$ (571) 443-0967 $|$ Atlanta, GA \\
    \href{https://namkhangnle.github.io/}{NamkhangNLe.github.io} $|$ \href{https://www.linkedin.com/in/namkhangnle/}{linkedin.com/in/NamkhangNLe}
\end{center}

\begin{flushleft}

\sectitle{Education}

\school{Georgia Institute of Technology}{August 2021 -- May 2025}
{\textbf{\textit{B.S. Computer Science, concentrations in Intelligence (AI/ML) and Information Internetworks}} \hfill 4.0/4.0 GPA \\ \textit{Relevant Coursework}: Data Structures \& Algorithms, Artificial Intelligence, Design \& Analysis of Algorithms, Computer Organization \& Programming, Probability \& Statistics, Combinatorics, Linear Algebra, Computer Systems \& Networks, Database Systems }

\sectitle{Experience}

    \begin{experience}{Citi}{Tampa, FL}{Software Engineer Intern}{June 2023 -- August 2023}
        \item Spearheaded Event Master Central, a full stack application for real-time corporate action event monitoring of financial assets in Angular \& Oracle Database increasing engineering awareness of deployment failures by 18\%.
        \item Revamped authentication logic, fortifying API token validation for REST API calls, contributing an 85\% uptime to production.
        \item Orchestrated seamless integration with Institutional Services Group's Cloud services using Spring Boot, optimizing performance through JSON-based HTTP requests, and enhancing overall efficiency by 15\% across the application.
        \item Leveraged 2 Python’s Pandas DataFrame to analyze surface temperatures vs global domestic product, resulting in a 0.8 positive correlation within Tableau in support of Citi's 1 trillion dollar commitment to sustainable finance.
    \end{experience}

    \begin{experience}{Lockheed Martin}{Manassas, VA}{Software Engineer Intern}{May 2022 -- August 2022}
        \item Trained a wildfire-based infrastructure identification AI model through Kubeflow, Pytorch, \& Tensorflow, with 98\% accuracy.
        \item Implemented a real-time data monitoring interface in Spring, driving a 20\% increase in operator awareness \& object tracking.
        \item Transformed codebase maintainability by converting logging levels from Apache Log4J to SLF4J, achieving 80\% code coverage.
        \item Collaborated with quality analysis team to execute comprehensive testing, resulting in a 12\% reduction in logging inefficiencies.
        
    \end{experience}

    \begin{experience}{Idaho National Laboratory}{Idaho Falls, ID}{Digital Animation Intern}{June 2021 -- May 2022}
        \item Championed the creation of 100 animations, capitalizing on a 20\% acceleration in midcareer transitions for nuclear engineers.
        \item Coordinated the production of over 10,000 digital frames for the generation of nuclear energy educational simulations.
        \item Drove cross-functional collaboration, working seamlessly with 10 designers and engineers for training material production.
    \end{experience}
    

\sectitle{Projects}

    \vspace{3pt}

    \begin{project}{Georgia Tech Computer Science Capstone Project}{https://github.com/NamkhangNLe/hemodynamics-calculator}{JavaScript, ReactJS, MongoDB, ExpressJS, NodeJS}{August 2023 -- Present}
        \item Developed a Hemodynamics Calculator, a full-stack application for the Emory University School of Medicine, to be used by 10 clinicians to reduce measurement error daily, impacting over 1,000 patients within the intensive care unit.
        \item Leveraged ReactJS, Express, and MongoDB to develop user-friendly interactive visualizations of trends in patient data and a reduction in data-related errors by 34\%.
    \end{project}

    \begin{project}{DiagnoseMe (Hackalytics Hackathon)}{https://devfolio.co/projects/diagnoseme-1992}{OpenAI ChatGPT, Google's Gemini, ElectronJS, Flask, ReactJS, }{February 2024}
        \item Constructed a ChatGPT powered ElectronJS application for disease diagnosis supporting medical students and doctors in training.
        \item Streamlined user experience by creating 120 unique prompt-engineered scenarios through Pandas DataFrame consolidation.
        \item Achieved a 15\% reduction in development time through REST APIs for seamless data exchange via JSON between React \& Flask.
    \end{project}

    \begin{project}{ScribbleTex (AI ATL Hackathon GitHub Winner)}{https://devpost.com/software/scribbletex}{JavaScript, Google Cloud Platform, VertexAI, Flask, ReactJS}{November 2023}
        \item Preprocessed 3 datasets comprising over 200,000 samples for the training of a custom machine learning model Scikit-learn.
        \item Developed a decision tree classifier and a convolutional neural network using Keras achieving a 97\% translation accuracy.
        \item Implemented a React-base frontend built using HTML, CSS, and JavaScript connected to a Python Flask backend with Rest API endpoints for optimized communication with the CNN model hosted on Google Cloud's Vertex AI platform.
    \end{project}

    \begin{project}{MorseTorch (HackGT Hackathon)}{https://devpost.com/software/morse-torch}{Swift, Python, Pandas, Jupyter Notebook, XCode, CoreML, Torch, Carthage}{October 2023}
        \item Employed Swift-based iOS application for Morse code translation, integrating Torch and Carthage binary framework.
        \item Executed K-means clustering algorithm using CoreML enabling real-time translation of optical signals with a 75\% accuracy rate.
        
    \end{project}

\sectitle{Skills}

    \vspace{3pt}
    \skill{Programming Languages}{Java, Python, C, SQL, JavaScript, CSS, HTML, Unified Modeling Language, C\#, R, Swift, LaTeX} \\
    \skill{Technologies}{Spring Boot, Angular, Android Studio, Bootstrap, RESTful APIs, Gradle, Pandas, Postman, React, Linux} \\
    \skill{Software Development}{Agile, Jira, CI/CD, DevSecOps, CLI, Confluence, Coverity, Jenkins, Artifactory, Unit Test, Git}\\
    \skill{Spoken Languages}{English (Native), Vietnamese (Fluent), Spanish (Limited Working Proficiency)} \\
    \skill{Affiliations}{Google Student Developer (Technical Lead), Competitive Programming, Mentor Jackets, Student Alumni Association}
    

\end{flushleft}

\end{document}
